Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS J08354256-0819237 and 2MASS J18212815+1414010

### 2016-12-14 ms.tex
I added an example corner plot of posterior distributions to the cosine fit.
I forced the appendex to be a page farther back and adjusted the number of significant digits in the corner plot.
I added some plots showing an example with a term cosine fit.

We extracted separate light curves for each target in 25 spectral bins of width 0.060~$\mu$m, as shown in Figure~\ref{fig:tserPfold}. Each of these were fit to a simple sinusoidal model:
\begin{equation}
F(t) = A \cos(2 \pi (t - t_0)/\tau) + B t + C
\end{equation}
Here, $F(t)$ is the flux as a function of time $t$, $A$ is the amplitude of periodic variations, $t_0$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
For the fits, we let $A$, $t_0$, $B$ and $C$ be free parameters, but fixed $\tau$ at the literature value of rotation period due to systematic trends (with a period of $\sim$24 hr) caused by uncorrected telluric variations.
We also imposed a prior that $A \geq 0$ so that solutions with a $\pi$ phase offset and negative amplitude were ignored.

@@

@@

>>>>

We extracted separate light curves for each target in 25 spectral bins of width 0.060~$\mu$m, as shown in Figure~\ref{fig:tserPfold}. Each of these were fit to a simple sinusoidal model:
\begin{equation}\label{eq:cosfit}
F(t) = A \cos(2 \pi (t - t_0)/\tau) + B t + C
\end{equation}
Here, $F(t)$ is the flux as a function of time $t$, $A$ is the amplitude of periodic variations, $t_0$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
For the fits, we let $A$, $t_0$, $B$ and $C$ be free parameters, but fixed $\tau$ at the literature value of rotation period due to systematic trends (with a period of $\sim$24 hr) caused by uncorrected telluric variations.
We also imposed a prior that $A \geq 0$ so that solutions with a $\pi$ phase offset and negative amplitude were ignored.

@@

\appendix
\clearpage
\pagebreak

@@

\section{Example Posterior Distributions}
\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{corner_example.pdf}
\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit} for the wavelength bin 1.08~$\mu$m.}\label{fig:postCosfit}
\end{centering}
\end{figure}

We also explore a 2 term sinusoidal fit:

\begin{equation}\label{eq:cosfit2term}
F(t) = A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) +  B t + C
\end{equation}

The 2 term fit works better on the light curves that show the variations at a high signal to noise ratio
\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{best_fit_2term.pdf}
\caption{Best fit model to time series at 1.08~$\mu$m using Equation \ref{eq:cosfit2term}.}\label{fig:model2Cosfit}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{corner_example.pdf}
\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit} for the wavelength bin 1.08~$\mu$m.}\label{fig:post2Cosfit}
\end{centering}
\end{figure}
